---
author: "Sangho Lee"
date: 7/11/2024
callout-appearance: minimal # this hides the blue "i" icon on .callout-notes
editor_options: 
  chunk_output_type: console
---


## Question 1: What key metrics would you propose to monitor over time to define the success of the team’s efforts in improving the revenue and why? Clearly define your metric(s) and explain how each is computed.

*<span style="color:blue;">Goal of the analysis: Design a statistically significant regression model that can reliably predict revenue, which will be used as a metric in later analysis. Additionally, identify key variables/drivers from the data that can be leveraged to improve revenue.</span>*

<br>

I will load the required packages to perform the analysis

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(readxl)
library(skimr)
library(caret)

```


To proceed, let's first examine the data.

:::: {.callout-note collapse="false"}
### Variable Definitions

    - Week ending: Ending date of a 7 day week
    - asin : Product Identification Number
    - orderedRevenueAmount: Revenue from that of the product
    - orderedUnits: Units sold of the product
    - ASP: Selling Price
    - Category: Identified category
    - subcategory: Identified sub category
    - Marketing spend: $ spent on marketing
    - Views: # views on the product

::::

```{r, warning=FALSE, message=FALSE}
belkin_data <- readRDS("belkin_data.rds")
belkin_data %>% 
  janitor::clean_names() %>% 
  dplyr::mutate(week_ending = as.Date(week_ending)) -> belkin_data


belkin_data %>% 
  DT::datatable(options = list(pageLength = 10))

```


<br>

Examining the dataset, I need to identify the response variable and determine the most suitable independent variables.

Before diving into the statistical modeling, I want to ensure the data is usable for analysis.

Let's review the data structure and check for any missing values

```{r}
belkin_data %>% skim()

```



#### Key Takeaways:

- The dataset is complete with no missing values.
- The asp column, while currently a character type, should be converted to numeric for analysis.
- The week_ending column is correctly formatted as a date.
- There are multiple unique categories and subcategories, which can be useful for detailed analysis.

<br>

##### Now that there is no missing data, and the data is well-cleaned and ready for use, I will compute the metrics I propose to monitor over time to evaluate the success of the team’s efforts in improving revenue.


Designing the linear regression model, as the response variable is a numeric revenue indicator.


```{r, message = FALSE, warning = FALSE}
model_data <- belkin_data %>%
  mutate(ordered_revenue_amount = as.numeric(ordered_revenue_amount),
         ordered_units = as.numeric(ordered_units),
         asp = as.numeric(asp),
         marketing_spend = as.numeric(marketing_spend),
         views = as.numeric(views),
         category = as.factor(category),
         subcategory = as.factor(subcategory),
         ordered_revenue_amount = as.numeric(ordered_revenue_amount),
         ordered_units = as.numeric(ordered_units),
         asp = as.numeric(asp),
         marketing_spend = as.numeric(marketing_spend),
         views = as.numeric(views))

model_data <- model_data %>%
  replace_na(list(ordered_revenue_amount = 0,
                  ordered_units = 0,
                  asp = 0,
                  marketing_spend = 0,
                  views = 0)) %>%
  mutate(across(everything(), ~ replace(.x, is.infinite(.x) | is.nan(.x), 0)))



# Create dummy variables for categorical predictors
data_dummies <- dummyVars(" ~ .", data = model_data)
data_prepared <- predict(data_dummies, newdata = model_data) %>% as.data.frame()

# Split the data into training and testing sets
set.seed(123)
trainIndex <- createDataPartition(data_prepared$ordered_revenue_amount, p = 0.8, list = FALSE, times = 1)
data_train <- data_prepared[trainIndex,]
data_test <- data_prepared[-trainIndex,]

# Build the regression model
model <- lm(ordered_revenue_amount ~ ., data = data_train)

options(scipen = 999)
summary(model)


```

#### Key Insights from the Model

Significant Predictors:

- asin: Coefficient = 0.0115, p-value < 0.0000000000000002
- ordered_units: Coefficient = 20.6753, p-value < 0.0000000000000002
- asp: Coefficient = 31.3739, p-value < 0.0000000000000002

Non-Significant Predictors:

- week_ending: Coefficient = -0.3642, p-value = 0.6245
- category.a: Coefficient = 30.4025, p-value = 0.7746
- category.b: Coefficient = -3.5281, p-value = 0.9735
- category.c: Coefficient = 180.2484, p-value = 0.0899
- subcategory.aa: Coefficient = -106.1723, p-value = 0.3708
- subcategory.bb: Coefficient = 164.3422, p-value = 0.1660
- subcategory.cc: Coefficient = 5.2521, p-value = 0.9646
- subcategory.dd: Coefficient = -21.0199, p-value = 0.8593
- marketing_spend: Coefficient = -0.0347, p-value = 0.2829
- views: Coefficient = 0.0794, p-value = 0.2408

Model Fit:
Adjusted R-squared: 0.4845 (moderate explanatory power)
Residual Standard Error: 4067 (moderate fit)

<br>

Refining the model by removing the non-significant predictors and re-evaluating the model fit.

```{r}
refined_model <- lm(ordered_revenue_amount ~ asin + ordered_units + asp, data = data_train)
summary(refined_model)


```

<br>


#### Key Points from the Model Summary

##### Significant Predictors:

- asin: Coefficient = 0.011480, p-value < 0.0000000000000002
- ordered_units: Coefficient = 20.671226, p-value < 0.0000000000000002
- asp: Coefficient = 31.411177, p-value < 0.0000000000000002

These predictors are highly significant (p-value < 0.001), indicating a strong relationship with ordered_revenue_amount.

Model Fit:

- Adjusted R-squared: 0.4844

This indicates that approximately 48.44% of the variance in ordered_revenue_amount is explained by the model.

- Residual Standard Error: 4068

This value indicates the average distance that the observed values fall from the regression line, showing a moderate fit.

- F-statistic: 3688, p-value < 0.00000000000000022
A high F-statistic and a very low p-value indicate that the model is statistically significant.


<br>


### Summary

We have successfully computed a significant linear regression model to determine the key predictors of revenue. The model identified ASIN, ordered units, and ASP as the most significant predictors.










