---
author: "Sangho Lee"
date: 7/12/2024
callout-appearance: minimal # this hides the blue "i" icon on .callout-notes
editor_options: 
  chunk_output_type: console
---


## Question 4: Please add visualizations please use a tool of your choice like python/Tableau/R and paste screenshots.

*<span style="color:blue;">Goal of the analysis: Conduct additional descriptive analysis on the dataset to uncover further insights.</span>*

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(DT)
library(readxl)
library(skimr)
library(caret)
library(knitr)
library(patchwork)

```

<br>





```{r, warning=FALSE, message=FALSE, include=FALSE}
belkin_data <- readRDS("belkin_data.rds")
belkin_data %>% 
  janitor::clean_names() %>% 
  dplyr::mutate(week_ending = as.Date(week_ending)) -> belkin_data


```


```{r, include = FALSE}
model_data <- belkin_data %>%
  mutate(ordered_revenue_amount = as.numeric(ordered_revenue_amount),
         ordered_units = as.numeric(ordered_units),
         asp = as.numeric(asp),
         marketing_spend = as.numeric(marketing_spend),
         views = as.numeric(views),
         category = as.factor(category),
         subcategory = as.factor(subcategory),
         ordered_revenue_amount = as.numeric(ordered_revenue_amount),
         ordered_units = as.numeric(ordered_units),
         asp = as.numeric(asp),
         marketing_spend = as.numeric(marketing_spend),
         views = as.numeric(views))

```

```{r, include=FALSE}
model_data <- model_data %>%
  replace_na(list(ordered_revenue_amount = 0,
                  ordered_units = 0,
                  asp = 0,
                  marketing_spend = 0,
                  views = 0)) %>%
  mutate(across(everything(), ~ replace(.x, is.infinite(.x) | is.nan(.x), 0)))

```


```{r, include = FALSE}
# Ensure numeric columns are properly formatted
belkin_data <- belkin_data %>%
  mutate(
    asp = as.numeric(asp),
    ordered_revenue_amount = as.numeric(ordered_revenue_amount),
    marketing_spend = as.numeric(marketing_spend),
    views = as.numeric(views)
  )
```


In this analysis, I will perform additional descriptive analysis to extract insights from the given data.

### 1. Revenue vs. Marketing Spend vs. Views

```{r, fig.width=10, fig.height=9, warning=FALSE, message=FALSE}
# Create scatter plot of Revenue vs Marketing Spend
p1 <- ggplot(belkin_data, aes(x = marketing_spend, y = ordered_revenue_amount, color = asp, size = views)) +
  geom_point(alpha = 0.6) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(title = "Revenue vs. Marketing Spend with ASP", x = "Marketing Spend ($)", y = "Revenue ($)", color = "ASP ($)") +
  theme_minimal()

# Create scatter plot of Revenue vs. Views, color-coded by Marketing Spend and size by ASP
p2 <- ggplot(belkin_data, aes(x = views, y = ordered_revenue_amount, color = marketing_spend, size = asp)) +
  geom_point(alpha = 0.7) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(title = "Revenue vs. Views with Marketing Spend and ASP",
       x = "Views",
       y = "Revenue ($)",
       color = "Marketing Spend ($)",
       size = "ASP ($)") +
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8))

# Combine the two plots into one screen
combined_plot <- p1 + p2 + plot_layout(ncol = 1, heights = c(1, 1))

# Display the combined plot
combined_plot
```



#### Revenue vs. Marketing Spend:

- Spread Across Spend: The marketing spend is distributed across the entire range from $0 to $5000, indicating a diverse allocation of marketing budgets across different products.
- Revenue Distribution: Revenue is mostly clustered at lower values, even with varying marketing spend levels. This suggests that high marketing spend does not always translate to higher revenue.
- ASP Impact: ASP ranges from $80 to $180, with clusters (in purplish color) around higher revenue values.

#### Revenue vs. Views:

- Views Distribution: The views range from 0 to 2000, showing that product visibility varies widely.
- Revenue Clustering: Similar to marketing spend, revenue is clustered at lower values regardless of the number of views
- Marketing Spend Clustering: Products with higher marketing spend are clustered around lower revenue values, indicating that increased marketing spend does not always lead to higher revenue.

#### Key Takeaways:

- Optimize Marketing Spend: Since revenue does not consistently increase with higher marketing spend, it's important to evaluate the effectiveness of marketing campaigns and reallocate budget towards more impactful strategies.

<br>





### 2. Revenue Over Time vs. Views Over Time


```{r, fig.width=10, fig.height=9, message = FALSE, warning = FALSE}
# Line plot of Revenue over Time
t1 <- belkin_data %>%
  mutate(week_ending = as.Date(week_ending)) %>%
  group_by(week_ending) %>%
  summarise(total_revenue = sum(ordered_revenue_amount)) %>%
  ggplot(aes(x = week_ending, y = total_revenue)) +
  geom_line(color = "blue") +
  labs(title = "Revenue Over Time", x = "Week Ending", y = "Total Revenue ($)") +
  theme_minimal()+
    theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))

# Line plot of Views Over Time
t2 <- belkin_data %>%
  mutate(week_ending = as.Date(week_ending)) %>%
  group_by(week_ending) %>%
  summarise(total_views = sum(views)) %>%
  ggplot(aes(x = week_ending, y = total_views)) +
  geom_line(color = "red") +
  labs(title = "Views Over Time",
       x = "Week Ending",
       y = "Total Views") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))

combined_plot_2 <- t1 / t2
combined_plot_2
```





#### January:
- Observation: High revenue despite stable views.
- Action: Analyze and replicate successful marketing strategies or promotions used in January to drive high revenue. Identify unique factors (e.g., post-holiday shopping) contributing to this performance.

#### February:
- Observation: Significant decline in revenue while views remain stable.
- Action: Investigate potential issues such as reduced marketing effectiveness, pricing changes, or external factors affecting consumer purchasing power. Adjust marketing efforts and pricing strategies to counteract the revenue decline.

#### April:
- Observation: Increased views but fluctuating revenue.
- Action: Optimize product listings, improve product descriptions, and ensure competitive pricing to convert higher views into actual sales. Evaluate the effectiveness of promotional campaigns to ensure they are converting views into purchases.

#### May:
- Observation: Continued increase in views but fluctuating revenue.
- Action: Enhance conversion rates by optimizing product listings, running targeted promotions, and providing incentives such as discounts or free shipping to encourage purchases.

#### June:
- Observation: Gradual increase in revenue despite a slight decline in views.
- Action: Maintain and further improve conversion rates by analyzing successful strategies implemented in June. Focus on sustaining this growth through continued marketing efforts, product improvements, and strategies to increase views.

#### Recommendations:
- Analyze January Strategies: Understand and replicate successful marketing strategies from January to boost revenue in other months.
- Address February Decline: Investigate and address factors contributing to the revenue decline in February. Adjust marketing and pricing strategies accordingly.
- Convert Views to Sales in April and May: Optimize product listings, run effective promotions, and provide incentives to convert higher views into sales during these months.
- Sustain Growth in June: Maintain and enhance successful strategies from June to ensure continued revenue growth.





